Making (Secure) FETCH Happen: \\ \vspace{2 mm} {\large End-to-End Metadata Security for IMAP}

### 2015-04-27 paper.tex
updated measurement graphs with all 77k messages

@@

The current version of IMAP is IMAP 4 revision 1 (IMAP4rev1). An IMAP client connects to an IMAP server over port 143, or over 993 if using SSL. The protocol allows a rich set of commands and actions, enabling clients to create, delete, and rename mailboxes, check for new messages, permanently remove messages, set and clear flags that facilitate multi-client synchronization, and more. Communication is structured in a command-response model, where all messages sent from the server are direct responses to requests from the client. Commands can be tagged with various labels, including OK to indicate success and BAD to indicate a malformed command, or they can be untagged. Many modern languages, including Python, include a library for sending commands to an IMAP server.

@@

\subsection{E2E Metadata Security for Transport}
While messaging applications have largely saturated the space of ways to ensure authentication and confidentiality, transport anonymity solutions are more well-developed in the Internet space. Tor, a system for anonymizing Internet traffic, sees about 2.5 million users per day \cite{torusers}. Anonymous remailers use Tor-like forwarding, but have not seen as wide adoption. Pond, a non-email messaging application, provides forward secure asynchronous messaging that does not leak traffic information ``except [to] a global passive attacker." \cite{pond}. There also exist SMTP servers that run as Tor hidden services, essentially bootstrapping their mail anonymity off of Tor's anonymity \cite{onionmail}.

@@

IMAP is a synchronization protocol that uses a central server to provide mail storage functionality to multiple clients. Popular mail providers such as Gmail, Yahoo! Mail, and Hotmail provide their users with both mail server and client functionality. \project assumes an untrusted network and an untrusted server, but a trusted client. The server does not guarantee availability, and may both passively analyze any data it is sent for timing or content information, and reply dishonestly to client requests. The IMAP servers of multiple users may collude. A network adversary, either passive or active, may collude with the adversary running the IMAP server. Either of these may themselves be users of \projectnospace, and attempt to gain information from communicating with a target user. All clients of the same account on a mail server have equivalent access privileges. These adversaries may attempt to determine the contents of a message, the communicants, and when a message was received (in order to determine the other two). We make the prior assumption that messages were initially sent to the client in a metadata-secure manner. A client should be able to identify and reject misinformation sent to it by the server.

@@

\section{Design overview}
To meet these requirements, we present \projectnospace, a client-only extension to the IMAP protocol that provides metadata privacy-preserving storage for multiple \project clients. In \projectnospace, emails received at the client are fully encrypted, including mail headers, indexed, and uploaded to a specialized folder in the IMAP server. This hides sender and recipient information from the IMAP server. Encryption is based on a passphrase and generated salt, using scrypt as a key derivation function. A special-use index message is stored in the folder as well, and tracks metadata for the client such as the apparent folder that a message is in (visible only to clients, not the server). A special-use lock message is used to allow multiple clients access to the same folder, in keeping with IMAP's design principles. Message arrival times are hidden from the server using a combination of scheduling, mixing, fake decoy messages, and techniques drawn from oblivious RAM. \project provides rollback detection for both messages and the index, using version numbers saved client-side and message hashes stored server-side. It is robust to client failure in any state.

@@

We can also see message interarrival times \--- that is, the distribution of the length of time between message arrivals and sends. Since this data was taken from the Gmail ``All Mail" folder, it includes both received and sent messages, as the set of all messages synchronized to an IMAP server would. Plotted on a linear scale, the ``long tail" distribution is once again evident; since it has an extremely high slope, we show it also on a logarithmic scale for clarity.

@@

In the \project protocol, a standard IMAP client library is wrapped with a \project module. An MUA then uses the \project module in lieu of a standard IMAP connection agent. The \project module will perform all necessary functions on behalf of the MUA, including encryption, UID translation, and metadata tracking. The IMAP server is unmodified.
% The \project protocol is 
% The core elements of the \project protocol are 
% \begin{enumerate*}[label=(\itshape\arabic*\upshape)]
% \item an \project module used in lieu of a standard IMAP connection agent in an MUA, and
% \item an index file that is stored as a regular message in a legacy IMAP server. \end{enumerate*}
As further described in later sections, the module ensures that metadata is encrypted along with message contents for all messages to be stored on the IMAP server. It also handles the indexing functions, mapping mailboxes to the messages they contain. This is a significant departure from the legacy system, where mailbox names and contents were exposed to the IMAP server. As such, it shifts the burden of tracking, updating, and syncing changes to the INDEX from the server to the client. When one client updates the INDEX, the IMAP server will see that a message has changed, and inform its other clients in the standard method.

@@

These changes permit the combination of MSMs and non-MSMs in the same storage system, ensuring an elegant transition to a more secure email.

\label{mail-from-secure}
\subsection{Mail From a Secure Source}
When email is received from a metadata-free source (SMTorP, DIME, Pond, etc.), it is stored in a ``cryptoblobs'' mailbox on the IMAP server that the client's \project module has set up. This change is then marked in the INDEX, which is correspondingly updated.

@@

\subsection{Command Translations}
The \project module sits between the client and the legacy IMAP module. It translates arguments, processes data, and returns results that give the client a pseudo-view of the contents of the IMAP server informed by the contents of the metadata INDEX. There are four possible mailbox classifications. The classification determines the actions that the module takes in response to each command. A PSEUDO mailbox is not mirrored in the IMAP server; it exists only in the INDEX and is thus only known to clients following the \project protocol. A HYBRID mailbox exists both in the IMAP server and in the INDEX. This is a mailbox such as INBOX, which must also be known the IMAP server as a location for the delivery of incoming messages. A PSEUDO/HIDDEN mailbox neither exists in the IMAP server nor is known to the client. It is for use only by the \project module. The FAKE\_MESSAGES mailbox used by the scheduler is an example of this type of mailbox. An ACTUAL/HIDDEN mailbox is known to the IMAP server but not to the \project client. The CRYPTOBLOBS mailbox, the mailbox in which all encrypted messages are stored on the IMAP server, is an example of this type of mailbox.

@@

\subsubsection{UIDVALIDITY} UIDVALIDITY is a mechanism for detecting non-persistence of message UIDs. \project does not allow UIDs to change over time, so as per the RFC, we may return `1' for any mailbox where we are handling UIDs \cite{rfc3501}.

@@

\subsubsection{LIST} The LIST command is used to recursively find all mailboxes in the server. The current prototype allows only top-level, no-children PSEUDO mailboxes. Thus, in translating LIST results, \project inserts PSEUDO mailbox results as if they were to exist at the top level. \project also removes HIDDEN folders from the LIST results before returning.

\label{uid-translation}
\subsection{UID Storage and Lookup}
While all encrypted messages are stored on the IMAP server in the CRYPTOBLOBS mailbox, the client's view should allow for a more complex representation of which messages are stored in which mailboxes. At a minimum, we would like to support an INBOX mailbox for messages that are received at the IMAP server, and an SMTorP or Pond folder for messages that are received at the client via a metadata-secure transport mechanism. Thus, each message needs an associated UID for its pseudo-mailbox, or the mailbox that the message is in as it appear to the client. But it also has an actual UID, or the UID inside the CRYPTOBLOBS mailbox. This UID is assigned by the IMAP server when \project APPENDs a message to a mailbox on the server. The APPEND command does not, however, return the assigned UID. Therefore we need a separate mechanism for associating a message's pseudo-UID with its actual UID.

To handle this, before appending a message to CRYPTOBLOBS, \project generates a 16-byte random UNIQUE SUBJECT number. This number is placed in the subject line of the appended message, forming an full subject line of the form ``ENCRYPTED <UNIQUE SUBJECT>". Then, when the client requests a message via a specific mailbox/UID pair, \project uses the INDEX to look up the UNIQUE SUBJECT for the pseudo-UID in the appropriate mailbox. It then searches for the message in CRYPTOBLOBS with UNIQUE SUBJECT in its subject line, which returns the unique actual UID of the message in the CRYPTOBLOBS mailbox.

@@

The lock recovery mechanism waits until a specified time (default 60 seconds), checking for the existence of the lock every few (default 2) seconds within that interval. After the time is completed, \project attempts to fetch the INDEX. If the index is not there, we assume that another client has failed and acquire the lock ourselves. If the index is there but has not been updated during that time (using the SEQUENCE NUMBER to determine this), we again acquire the lock. Yet if the index is there and has been updated, we assume someone else is still using the lock and double the total wait time until our next check.

\subsection{Deletion}
Various \project actions include deletion of a message from the CRYPTOBLOBS mailbox. In general, not deleting a message will not leak any data to the IMAP server, since our threat model includes a server than can either refuse to delete or can save a backup version of any message. Yet for practical reasons such as mailbox data usage and lack of clutter, it is generally beneficial to at least attempt to delete a message. Here we must note that IMAP servers may differ in their implementation in regard to the location of messages, potentially complicating deletion protocols. For example, Gmail uses its All Mail mailbox (``label'', in their terms) as a message archive \cite{allmail}. That is, if a message appears in any mailbox, it will also appear in the All Mail mailbox. If it is deleted from All Mail but still exists elsewhere, it will be replaced in All Mail. Thus, to delete a message from any non-All Mail mailbox, it must first be deleted from all other mailboxes then deleted from All Mail. Note that the message will be assigned a different UID for each mailbox that it appears in.

@@

\label{rollback}
\subsection{Rollback Detection}
While we cannot rely on the IMAP server for availability, we can detect and decline to accept rollback of any part of the system. Each time that the INDEX is updated by any client, its SEQUENCE NUMBER is incremented. Thus, when a new INDEX is downloaded, the \project module compares the SEQUENCE NUMBER of the received INDEX to the most recent SEQUENCE NUMBER. If the downloaded sequence number is not at least the value of the SEQUENCE NUMBER known to the client, then the new index is not accepted. It saves this in memory, but also stores it to a local file specified by the client of the module. When a client first connects to an IMAP server that has already been initialized, it uses the current INDEX's SEQUENCE NUMBER as the initial number.

@@

\section{Protecting Metadata}
Once a message has been received at the client, we would like to upload it to the IMAP server for storage. Yet while we can hide the FROM and TO headers easily, we do not want the server to gain timing information about the message. If we upload it immediately, then the server will know that we have received a message at that time. Even worse, modern clients often save sent messages to a Sent Messages folder. If the mail server of the sender and the receiver are colluding, as can easily be the case when both clients are using the same company to provide servers, then the server could easily execute timing attacks by observing two users suspecting to be communicating, and seeing if they upload a message at about the same time. So, we must include a mechanism for hiding this timing metadata from the IMAP server. The solution must not allow the server to recover the timing information, it must not take up extraneous amount of space in the mailbox, and it must allow sufficiently frequent and short exchanges with the server. Additionally, for any of these methods, the deletion of a message from the server must not reveal otherwise hidden information.

\subsection{Mechanisms}
While we can vary particular parameters and algorithms, most rely on two primary components, scheduling and mixing.

@@

ORAM makes assumptions that we could perhaps consider relaxing. First, ORAM assumes constant, fixed-size blocks of memory. Messages in a mail server need not be constant size, although any solution that involves mixing will require elements of the mix to all be of the same size. Second, a primary goal of ORAM is to hide correlated memory locations. If messages are not decomposed into fixed-size chunks and all saved into the same pseudo-mailbox, then an individual message is not correlated with any other message. Note that mixing will generally require chunking of messages, and we wish to support multiple pseudo-folders, but locations are not as inherently correlated in all cases as they are when a program is executing on memory locations. Third, mailboxes do not allow store operations in the sense of RAM; IMAP only supports appending to mailboxes. Even under these relaxations, most solutions that do not implement an ORAM-adherent technique will trade off either functionality or security.

>>>>

solution: summary of what I'm trying to do, how it will appear to a target user who is (decsription of target user)

@@

The current version of IMAP is IMAP 4 revision 1 (IMAP4rev1). An IMAP client connects to an IMAP server over port 143, or over 993 if using SSL. The protocol allows a rich set of commands and actions, enabling clients to create, delete, and rename mailboxes, check for new messages, permanently remove messages, set and clear flags that facilitate multi-client synchronization, and more. Communication is structured in a command-response model, where all messages sent from the server are direct responses to requests from the client. Commands can be tagged with various labels, including OK to indicate success and BAD to indicate a malformed command, or they can be untagged. While not explicitly required by the protocol, a standard client implementation will use the provided commands to locally duplicate the server's state, thereby causing state to be replicated across the server and one or more clients, with all clients synchronized via the server. Many modern languages, including Python, include a library for sending commands to an IMAP server.

@@

\subsection{E2E Metadata Security for Transport}
While messaging applications have largely saturated the space of ways to ensure content confidentiality and communicants authentication, metadata security requires an additional layer of protection. For example, if we were to see the following inbox contents, we do not need to see the contents of the emails to gain some understanding of the events that transpired.

\includegraphics[width=\textwidth]{planned}

Who a person is communicating with and when they do so can reveal as much information, if not more, than the contents of the messages. But it is difficult to secure metadata. Communication protocols generally rely on the inclusion of a FROM header to know the return address, as well as to prevent spam. And the server that delivered a message will certainly know when it was delivered, as well, meaning that an observer with the ability to correlate the timing of messages can recover the identities of the communicants. To achieve metadata-security, a protocol that is oblivious to the sender's identity must include a solution for spam mitigation, such as a proof-of-work algorithm. It must also provide some anonymity in its routing.

These challenges have been addressed more thoroughly in the space of providing transport anonymity, and particularly for Internet routing. Tor, a system for anonymizing Internet traffic, sees about 2.5 million users per day \cite{torusers}. Anonymous remailers use Tor-like forwarding, but have not seen as wide adoption. Pond, a non-email messaging application, provides forward secure asynchronous messaging that does not leak traffic information ``except [to] a global passive attacker." \cite{pond}. There also exist SMTP servers that run as Tor hidden services, essentially bootstrapping their mail anonymity off of Tor's anonymity \cite{onionmail}.

@@

IMAP is a synchronization protocol that uses a central server to provide mail storage functionality to multiple clients. Popular mail providers such as Gmail, Yahoo! Mail, and Hotmail provide their users with both mail server and client functionality. \project assumes an untrusted network and an untrusted server, but a trusted client. The attacker controls the server, so we do not expect it to guarantee availability. The attacker may both passively analyze any data it is sent for timing or content information, and reply dishonestly to client requests. The IMAP servers of multiple users may collude. A network adversary, either passive or active, may collude with the adversary running the IMAP server. Either of these may themselves be users of \projectnospace, and attempt to gain information from communicating with a target user. All clients of the same account on a mail server have equivalent access privileges. These adversaries may attempt to determine the contents of a message, the communicants, and when a message was received (in order to determine the other two). We make the prior assumption that messages were initially sent to the client in a metadata-secure manner. A client should be able to identify and reject misinformation sent to it by the server.

@@

\section{Design overview}
To meet these requirements, we present \projectnospace, a client-only extension to the IMAP protocol that provides metadata privacy-preserving storage for multiple \project clients. In \projectnospace, emails received at the client are fully encrypted, including mail headers, indexed, and uploaded to a specialized mailbox in the IMAP server. This hides sender and recipient information from the IMAP server. Encryption is based on a passphrase and generated salt, using scrypt as a key derivation function. A special-use index message is stored in the mailbox as well, and tracks metadata for the client such as the apparent mailbox that a message is in (called a pseudo-mailbox, and visible only to clients, not the server). A special-use lock message is used to allow multiple clients access to the same mailbox, in keeping with IMAP's design principles. Message arrival times are hidden from the server using a combination of scheduling, mixing, fake decoy messages, and techniques drawn from oblivious RAM. \project provides rollback detection for both messages and the index, using version numbers saved client-side and message hashes stored server-side. It is robust to client failure in any state.

@@

We can also see message interarrival times \--- that is, the distribution of the length of time between message arrivals and sends. Since this data was taken from the Gmail ``All Mail" mailbox, it includes both received and sent messages, as the set of all messages synchronized to an IMAP server would. Plotted on a linear scale, the ``long tail" distribution is once again evident; since it has an extremely high slope, we show it also on a logarithmic scale for clarity.

@@

In the \project protocol, a standard IMAP client library is wrapped with a \project module. An MUA then uses the \project module in lieu of a standard IMAP connection agent. The \project module will perform all necessary functions on behalf of the MUA, including encryption, UID translation, and metadata tracking. The IMAP server is unmodified.
% The \project protocol is 
% The core elements of the \project protocol are 
% \begin{enumerate*}[label=(\itshape\arabic*\upshape)]
% \item an \project module used in lieu of a standard IMAP connection agent in an MUA, and
% \item an index file that is stored as a regular message in a legacy IMAP server. \end{enumerate*}
As further described in later sections, \project ensures that metadata is encrypted along with message contents for all messages to be stored on the IMAP server. It also handles the indexing functions, mapping pseudo-mailboxes to the messages they contain. This is a significant departure from the legacy system, where mailbox names and contents were exposed to the IMAP server. As such, it shifts the burden of tracking, updating, and syncing changes to the INDEX from the server to the client. When one client updates the INDEX, the IMAP server will see that a message has changed, and inform its other clients in the standard method.

@@

These changes permit the combination of MSMs and non-MSMs in the same storage system, ensuring an elegant transition to a more secure email. While both types of messages can coexist under \project architecture, the pathways that they traverse to enter the system are distinct. In the next two subsections, we will discuss separately the receipt and insertion methods for messages received via legacy SMTP and for messages received from an alternative metadata-secure transport.

\label{mail-from-secure}
\subsection{Mail From a Secure Source}

When email is received from a metadata-free source (SMTorP, DIME, Pond, etc.), it is stored in a ``cryptoblobs'' mailbox on the IMAP server that the client's \project module has set up. This change is then marked in the INDEX, which is correspondingly updated.

@@

\subsection{Command Translations}
The \project module sits between the client and the legacy IMAP module. It translates arguments, processes data, and returns results that give the client a pseudo-view of the contents of the IMAP server informed by the contents of the metadata INDEX. There are four possible pseudo-mailbox classifications. The classification determines the actions that the module takes in response to each command. A PSEUDO mailbox is not mirrored in the IMAP server; it exists only in the INDEX and is thus only known to clients following the \project protocol. A HYBRID mailbox exists both in the IMAP server and in the INDEX. This is a mailbox such as INBOX, which must also be known the IMAP server as a location for the delivery of incoming messages. A PSEUDO/HIDDEN pseudo-mailbox neither exists in the IMAP server nor is known to the client. It is for use only by the \project module. The FAKE\_MESSAGES pseudo-mailbox used by the scheduler is an example of this type of pseudo-mailbox. An ACTUAL/HIDDEN mailbox is known to the IMAP server but not to the \project client. The CRYPTOBLOBS mailbox, the mailbox in which all encrypted messages are stored on the IMAP server, is an example of this type of mailbox.

@@

\subsubsection{UIDVALIDITY} UIDVALIDITY is a mechanism for detecting non-persistence of message UIDs. \project does not allow UIDs to change over time, so as per the RFC, we may return `1' for any mailbox where we are handling UIDs, pseudo or actual \cite{rfc3501}.

@@

\subsubsection{LIST} The LIST command is used to recursively find all mailboxes in the server. The current prototype allows only top-level, no-children PSEUDO mailboxes. Thus, in translating LIST results, \project inserts PSEUDO mailbox results as if they were to exist at the top level. \project also removes HIDDEN mailboxes from the LIST results before returning.

\label{uid-translation}
\subsection{UID Storage and Lookup}
While all encrypted messages are stored on the IMAP server in the CRYPTOBLOBS mailbox, the client's view should allow for a more complex representation of which messages are stored in which mailboxes. At a minimum, we would like to support an INBOX mailbox for messages that are received at the IMAP server, and an SMTorP or Pond pseudo-mailboxes for messages that are received at the client via a metadata-secure transport mechanism. Thus, each message needs an associated UID for its pseudo-mailbox, or the mailbox that the message is in as it appear to the client. But it also has an actual UID, or the UID inside the CRYPTOBLOBS mailbox. This UID is assigned by the IMAP server when \project APPENDs a message to a mailbox on the server. The APPEND command does not, however, return the assigned UID. Therefore we need a separate mechanism for associating a message's pseudo-UID with its actual UID.

To handle this, before appending a message to CRYPTOBLOBS, \project generates a 16-byte random UNIQUE SUBJECT number. This number is placed in the subject line of the appended message, forming an full subject line of the form ``ENCRYPTED <UNIQUE SUBJECT>". Then, when the client requests a message via a specific mailbox/UID pair, \project uses the INDEX to look up the UNIQUE SUBJECT for the pseudo-UID in the appropriate pseudo-mailbox. It then searches for the message in CRYPTOBLOBS with UNIQUE SUBJECT in its subject line, which returns the unique actual UID of the message in the CRYPTOBLOBS mailbox.

@@

The lock recovery mechanism waits until a specified time (default 60 seconds), checking for the existence of the lock every few (default 2) seconds within that interval. After the time is completed, \project attempts to fetch the INDEX. If the index is not there, we assume that another client has failed and acquire the lock ourselves. If the index is there but has not been updated during that time (using the SEQUENCE NUMBER to determine this), we again acquire the lock. Yet if the index is there and has been updated, we assume someone else is still using the lock and double the total wait time until our next check. This mechanism could create a race condition in re-creating a lost LOCK, when multiple waiting clients fulfil their LOCK re-acquisition conditions simultaneously and therefore both attempt to take the LOCK themselves. We could address this in various manners. \project could decouple LOCK acquisition and recovery mechanisms, or partially decouple them by recreating a lost LOCK, waiting, then acquiring it. Additionally, \project could mitigate simultaneity by waiting a randomized time selected from an exponential distribution before acquiring a lost LOCK, so that multiple waiting clients are less likely to do simultaneous re-creations.

\subsection{Deletion}
Various \project actions include deletion of a message from the CRYPTOBLOBS mailbox. In general, not deleting a message will not leak any data to the IMAP server, since our threat model includes a server than can either refuse to delete or can save a backup version of any message. Yet for practical reasons such as server data usage and lack of clutter, it is generally beneficial to at least attempt to delete a message. Here we must note that IMAP servers may differ in their implementation in regard to the location of messages, potentially complicating deletion protocols. For example, Gmail uses its All Mail mailbox (``label'', in their terms) as a message archive \cite{allmail}. That is, if a message appears in any mailbox, it will also appear in the All Mail mailbox. If it is deleted from All Mail but still exists elsewhere, it will be replaced in All Mail. Thus, to delete a message from any non-All Mail mailbox, it must first be deleted from all other mailboxes then deleted from All Mail. Note that the message will be assigned a different UID for each mailbox that it appears in.

@@

\label{rollback}
\subsection{Rollback Detection}
While we cannot rely on the IMAP server for availability, we can detect and decline to accept rollback of any part of the system. In a rollback attack, an adversary in control of the server can partially or completely snapshot the files on the server at any given time, then later replace a file with that name with the old contents. So, if the server took a snapshot of one version of the INDEX, then a client changes the INDEX to reflect deletion of a message, the server could later replace the current INDEX with the previous one, making it appear as though the message had not been deleted. This would be particularly problematic if a unique subject is reused, which could cause a client to receive a different message for that subject than they should have seen.

 Each time that the INDEX is updated by any client, its SEQUENCE NUMBER is incremented. Thus, when a new INDEX is downloaded, the \project module compares the SEQUENCE NUMBER of the received INDEX to the most recent SEQUENCE NUMBER. If the downloaded sequence number is not at least the value of the SEQUENCE NUMBER known to the client, then the new index is not accepted. It saves this in memory, but also stores it to a local file specified by the client of the module. When a client first connects to an IMAP server that has already been initialized, it uses the current INDEX's SEQUENCE NUMBER as the initial number.

@@

\section{Protecting Metadata}
Once a message has been received at the client, we would like to upload it to the IMAP server for storage. Yet while we can hide the FROM and TO headers easily, we do not want the server to gain timing information about the message. If we upload it immediately, then the server will know that we have received a message at that time. Even worse, modern clients often save sent messages to a Sent Messages mailbox. If the mail server of the sender and the receiver are colluding, as can easily be the case when both clients are using the same company to provide servers, then the server could easily execute timing attacks by observing two users suspected to be communicating, and seeing if they upload a message at about the same time. So, we must include a mechanism for hiding this timing metadata from the IMAP server. The solution must not allow the server to recover the timing information, it must not take up extraneous amount of space in the mailbox, and it must allow sufficiently frequent and short exchanges with the server. Additionally, for any of these methods, the deletion of a message from the server must not reveal otherwise hidden information.

\subsection{Mechanisms}
While we can vary particular parameters and algorithms, most rely on two primary components, scheduling and mixing. By scheduling, we mean that the client will exchange data with the server on a set or randomized schedule. By mixing, we mean that in an exchange with the server, multiple messages will be deleted, and multiple messages uploaded in their place, with only the client being aware of the correlations between messages deleted and uploaded.

@@

ORAM makes assumptions that we could perhaps consider relaxing. First, ORAM assumes constant, fixed-size blocks of memory. Messages in a mail server need not be constant size, although any solution that involves mixing will require elements of the mix to all be of the same size. Second, a primary goal of ORAM is to hide correlated memory locations. If messages are not decomposed into fixed-size chunks and all saved into the same pseudo-mailbox, then an individual message is not correlated with any other message. Note that mixing will generally require chunking of messages, and we wish to support multiple pseudo-mailboxes, but locations are not as inherently correlated in all cases as they are when a program is executing on memory locations. Third, mailboxes do not allow store operations in the sense of RAM; IMAP only supports appending to mailboxes. Even under these relaxations, most solutions that do not implement an ORAM-adherent technique will trade off either functionality or security.
